Comparative Evaluation of Spark and Flink Stream Processing

### 2017-02-19 paper/paper.tex
added spark section

\par The processing models of Big Data are Batch and Stream processing, Batch processing is a way to handle large volumes of data (e.g., processing of historical transactions), is more concerned with throughput. While the Stream processing  is to manages fast and continuously incoming data (real-time), processes it as it arrives (e.g., credit card fraud detection and network monitoring applications), where the low latency is required.

\par The purpose of this paper is to provide a comparative experimental evaluation of throughput, latency (i.e., performance) of stream processing in Apache Spark and Apache Flink. We use a dataset of airplanes trajectories provided in the context of Datacron project\footnote{\url{http://www.datacron-project.eu/}}, in order to simulate real-world use cases. Using multiple streaming data workloads we try to cover the main programming API differences between the both frameworks. Informally,  this work aims to help developer to determine which platform to choose in production.

@@

\section{Technical Background}
This section presents the main characteristics, APIs, and main data abstraction of Spark and Flink.

\section{Experiment Setup and Implementation}
This section describes the experiment workloads and their implementation in each framework.
\section{Performance Results}

@@

%
\end{thebibliography}
\end{document}

>>>>

\par The processing models of Big Data are Batch and Stream processing, Batch processing is a way to handle large volumes of data (e.g., processing of historical transactions), is more concerned with throughput. While the Stream processing  is a method to manage fast and continuously incoming data (real-time), process it as it arrives (e.g., credit card fraud detection and network monitoring applications), where the low latency is required. The variety of data (structured and semi-structured) is included in the two processing models.

\par The purpose of this paper is to provide a comparative experimental evaluation of throughput, latency (i.e., performance) of stream processing in Apache Spark and Apache Flink. We use a datasets of airplanes trajectories provided in the context of Datacron project\footnote{\url{http://www.datacron-project.eu/}}, in order to simulate real-world use cases. Using multiple streaming data workloads we try to cover the main programming API differences between the both frameworks. Informally,  this work aims to help developer to determine which platform to choose in production.

@@

\section{Technical Background}
 In this section, we present the architecture, key characteristics, programming APIs  of Apache Spark, Apache Flink. The Apache Kafka platform is also discussed briefly.

\subsection{Apache Spark}

Apache Spark is an open source project that provide general framework for large-scale data processing \cite{spark}. It offers programming API in Java, Scala, Python and R. Its stack includes set of built-in modules including Spark SQL, MLlib for machine learning, GraphX for graph processing, and Spark Streaming to process real-time data streams. It can access different data sources including Hadoop Distributed File System (HDFS), Apache Cassandra database, Apache HBase database etc.

The main data abstraction in Spark is the Resilient Distributed Datasets (RDDs), which is a in-memory collection of elements partitioned across cluster of computers that can be processed in parallel \cite{rdd}. RDDs supports two categories of operations: transformations that drive new RDDs from the operated ones (e.g., map).  And actions which return a value (e.g., count).
\section{Experiment Setup and Implementation}
This section describes the experiment workloads and their implementation in each framework.
\section{Performance Results}

@@

\bibitem[2]{spark} 
Apache Spark. Available: https://spark.apache.org/ [Accessed February 2017]

\bibitem[3]{rdd}
Zaharia, Matei, et al. "Resilient distributed datasets: A fault-tolerant abstraction for in-memory cluster computing." Proceedings of the 9th USENIX conference on Networked Systems Design and Implementation. USENIX Association, 2012.
%
\end{thebibliography}
\end{document}
